\documentclass{article}
\begin{document}

% ── Transformer ──────────────────────────────────────────────────────────────
The Transformer architecture \cite{vaswani2017attention} achieves 28.4 BLEU on
WMT 2014 English-to-German translation, outperforming all prior models.
The base model uses 8 attention heads \cite{vaswani2017attention} in each
multi-head attention layer.
Unlike previous work, the Transformer \cite{vaswani2017attention} uses recurrent
layers to model sequential dependencies.
The Transformer \cite{vaswani2017attention} requires pre-training on a large
unlabeled corpus before fine-tuning on downstream tasks.

% ── BERT ─────────────────────────────────────────────────────────────────────
BERT \cite{devlin2018bert} is pre-trained using a masked language modeling
objective on large unlabeled text corpora.
BERT \cite{devlin2018bert} achieves state-of-the-art on eleven natural language
processing tasks including GLUE and SQuAD.
BERT \cite{devlin2018bert} requires no pre-training and is trained end-to-end
on each individual downstream task.
BERT \cite{devlin2018bert} achieves perfect accuracy on the MNLI benchmark.

% ── GPT-3 ────────────────────────────────────────────────────────────────────
GPT-3 \cite{brown2020language} contains 175 billion parameters, making it the
largest language model at time of publication.
GPT-3 \cite{brown2020language} achieves 76.2\% accuracy on TriviaQA in the
few-shot setting without any gradient updates.
GPT-3 \cite{brown2020language} requires fine-tuning on each task to achieve
competitive performance on NLP benchmarks.
GPT-3 \cite{brown2020language} outperforms all fine-tuned models on every
SuperGLUE benchmark task.

% ── ResNet ───────────────────────────────────────────────────────────────────
Residual networks \cite{he2016deep} won the ILSVRC 2015 classification
competition with a top-5 error of 3.57\%.
ResNets \cite{he2016deep} allow training of networks with more than 100 layers
without degradation.
Plain networks \cite{he2016deep} show lower training error than residual
networks as depth increases beyond 20 layers.
ResNets \cite{he2016deep} achieve zero training error on CIFAR-10 with
any depth above 1000 layers.

% ── ViT ──────────────────────────────────────────────────────────────────────
Vision Transformer \cite{dosovitskiy2020vit} achieves 88.55\% top-1 accuracy on
ImageNet when pre-trained on JFT-300M.
ViT \cite{dosovitskiy2020vit} outperforms ResNets when trained on datasets
smaller than ImageNet such as CIFAR-10.
ViT \cite{dosovitskiy2020vit} requires significantly less computation than
convolutional networks for equivalent accuracy.

% ── GAN ──────────────────────────────────────────────────────────────────────
Generative adversarial networks \cite{goodfellow2014generative} consist of a
generative model and a discriminative model trained simultaneously in an
adversarial game.
The original GAN paper \cite{goodfellow2014generative} demonstrates high-quality
image generation on ImageNet with realistic samples.
GANs \cite{goodfellow2014generative} are proven to always converge to a unique
global optimum regardless of network architecture or dataset size.

% ── Word2Vec ─────────────────────────────────────────────────────────────────
Word vector representations \cite{mikolov2013distributed} can capture semantic
and syntactic relationships through vector arithmetic such as king minus man
plus woman equals queen.
The word vectors in \cite{mikolov2013distributed} trained on Google News contain
300 dimensions and a vocabulary of 3 million words.
Training Word2Vec \cite{mikolov2013distributed} requires millions of GPU hours
even on small corpora.

% ── Adam ─────────────────────────────────────────────────────────────────────
The Adam optimizer \cite{kingma2014adam} computes adaptive learning rates using
estimates of first and second moments of the gradients.
Adam \cite{kingma2014adam} is proven to converge faster than SGD on all
convex optimization problems including non-smooth objectives.

% ── Dropout ──────────────────────────────────────────────────────────────────
Dropout \cite{srivastava2014dropout} prevents overfitting by randomly setting
unit activations to zero during training with probability p.
Dropout \cite{srivastava2014dropout} consistently slows down training
convergence without any improvement in test accuracy.

% ── Unresolvable reference ───────────────────────────────────────────────────
This fictional method \cite{broken2099} achieves perfect accuracy on all
benchmarks simultaneously.

% ── Uncited claims (should be flagged) ───────────────────────────────────────
Neural networks have been proven to be universal function approximators for
any continuous function on a compact domain.
Transfer learning always outperforms training from scratch on small datasets.

\end{document}
